The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-07 paper.qmd
Fixed vizumap issue

# load Libraries
library(tidyverse)
library(biscale)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)

# Broom returns an error with Vizumap, run this if can't compile
# devtools::install_version(package = "broom", version = "1.0.4")
```

@@

pix_a <- pixelate(pixel_2a, pixelSize = 3, id = "my_id")

@@

pix_b <- pixelate(pixel_2b, pixelSize = 3, id = "my_id")

>>>>

# load Libraries
library(tidyverse)
library(biscale)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)
```

@@

pix_a <- pixelate(pixel_2a, pixelSize = 70, id = "my_id")

@@

pix_b <- pixelate(pixel_2b, pixelSize = 70, id = "my_id")
